---
title: "Exercise Sheet 3"
author: "Anika Kind (12767778)"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1: Initializing git

### c)

Strengths 

- great for collaboration

- very hard to lose files

Weaknesses

- can be complicated to use

- Struggles with large files

## Exercise 2: Putting your Repository on GitHub

### a)

https://github.com/AnikaTabea/exeRcise-sheet-3/blob/main/Ex_3.Rmd

## Exercise 3: Pixar Films

### a)

```{r}
library(tidyverse)
```

```{r}
pixar_films <- read_csv("data/pixar_films.csv")

pixar_films <- pixar_films %>% 
  filter(!is.na(film))

pixar_films$film_rating <- as.factor(pixar_films$film_rating)

```

film_rating: 

- G: General Audiences. This means, all ages are admitted.

- PG: Parental Guidance Suggested. This means, some material may not be suitable for children.

The factor data type is suitable for categorical variables. This means variables with a finite number of repeating values. In this case, these are the values G and PG, which are repeated.

### b)

```{r}
film_series <- data.frame(
  title = c("Toy Story", "Cars", "Incredibles", "Finding Nemo/ Dori"),
  number_of_movies = c("4", "3", "2", "2")
)

View(film_series)
```

### c)

```{r}
public_response <- read_csv("data/public_response.csv")

public_response$cinema_score <- factor(public_response$cinema_score,
                                       levels = c("A-", "A", "A+"),
                                       ordered = TRUE)

merged_data <- merge(public_response, pixar_films, by = "film")

head(merged_data)

```

### d)

```{r}
library(ggplot2)
library(dplyr)

cinema_levels <- c("A-", "A", "A+")
public_response$cinema_score <- factor(public_response$cinema_score, 
                                       levels = cinema_levels, 
                                       ordered = TRUE)

public_response$series <- case_when(
  grepl("Toy Story", public_response$film) ~ "Toy Story",
  grepl("Cars", public_response$film) ~ "Cars",
  grepl("Monsters", public_response$film) ~ "Monsters",
  grepl("Finding", public_response$film) ~ "Finding Nemo",
  grepl("Incredibles", public_response$film) ~ "Incredibles",
  TRUE ~ "Standalone"
)

filtered_data <- public_response %>%
  filter(!is.na(cinema_score) & series != "Standalone")

filtered_data$cinema_score_numeric <- as.numeric(filtered_data$cinema_score)

ggplot(filtered_data, aes(x = series, y = cinema_score_numeric, fill = film)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  scale_y_continuous(breaks = 1:3, labels = cinema_levels) +
  labs(title = "CinemaScore Ratings by Pixar Film Series",
       x = "Film Series",
       y = "Cinema Score",
       fill = "Film") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

In general, there is no clear pattern. In three series, the second movie has the highest rating. In the Incredibles series, both films are rated A+. In the Cars series, the first and third movies are rated A, while the second movie is rated A-.


