---
title: "Exercise Sheet 3"
author: "Anika Kind (12767778)"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1: Initializing git

### c)

Strengths 

- great for collaboration

- very hard to lose files

Weaknesses

- can be complicated to use

- Struggles with large files

## Exercise 2: Putting your Repository on GitHub

### a)

https://github.com/AnikaTabea/exeRcise-sheet-3/blob/main/Ex_3.Rmd

## Exercise 3: Pixar Films

### a)

```{r}
library(tidyverse)
```

```{r}
pixar_films <- read_csv("data/pixar_films.csv")

pixar_films <- pixar_films %>% 
  filter(!is.na(film))

pixar_films$film_rating <- as.factor(pixar_films$film_rating)

```

film_rating: 

- G: General Audiences. This means, all ages are admitted.

- PG: Parental Guidance Suggested. This means, some material may not be suitable for children.

The factor data type is suitable for categorical variables. This means variables with a finite number of repeating values. In this case, these are the values G and PG, which are repeated.

### b)

```{r}
film_series <- data.frame(
  title = c("Toy Story", "Cars", "Incredibles"),
  number_of_movies = c("4", "3", "2")
)

View(film_series)
```

### c)

```{r}
public_response <- read_csv("data/public_response.csv")

public_response$cinema_score <- factor(public_response$cinema_score,
                                       levels = c("A-", "A", "A+"),
                                       ordered = TRUE)

merged_data <- merge(public_response, pixar_films, by = "film")

head(merged_data)

```



